Interpreting Random Forest Predictions for Firearm Identification Using LIME

### 2018-11-02 paper/paper.Rmd
copied and pasted lime procedure - now need to work on this

(fill in once the new random forest model has been fit)

@@

>>>>

@@

Step 0: Split iris data into training and testing datasets
Step 1: Fit a complex model to the training data
Step 2: Obtain distributions of the variables from the training data
Step 3: Sample from each of the variable distributions $n$ times
Step 4: Obtain predictions for sampled values using the complex model
For each testing case use the random forest model to make a prediction for each of the $n=5000$ samples
In the iris data, the predictions are represented by the probability that a flower is a particular species
Step 5: Obtain similarity score between data observation and sampled values
LIME uses exponential kernel function
  ...
where
$x_{obs}$: observed data vector to predict
$x_{sampled}$: sampled data vector from distribution of training variables
$D(\cdot, \cdot)$: distance function such as euclidean distance, cosine distance, etc.
$\sigma$: width (default set to 0.75 in lime)
Step 6: Perform feature selection by fiting a model to the sampled data and associated predictions (weighted by the similarity scores)
The user can specify the number of variables (features) they would like to select: $m$
With the iris data, the following three models will be fit to perform variable selection to select $m=2$ features:
To perform variable selection lime supports: 
 forward selection with ridge regression
 highest weight with ridge regression
 LASSO
 tree models
auto: forward selection if $m\le6$, highest weight otherwise
Step 7: Fit a simple model to regress the predictions on the $m$ selected predictor variables (weighted by the similarity scores)
Currently, `lime` is programmed to use ridge regression as the simple model
If the response is categorical, the user can select how many categories they want to explain
In this example, only setosa will be explained
If petal length and sepal length were selected as the most important features for the first case in the testing data, then the simple model is
Step 8: Extract the feature weights and use them as the explanations
